Intelligent Reflecting Surface-Aided SWIPT: Joint Waveform, Active and Passive Beamforming Design

### 2021-04-11 assets/waveform_subband.tex
:bento: Update assets

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,3.503in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	2.82172700965795\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_I$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000289213065829642\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_P$}

@@

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,2.747in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.295470946033806\\
2	2.78041553969328\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	6.88515292983531e-06\\
2	7.11243494475005e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.992in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00886602819700381\\
2	0.0237787230194659\\
3	0.108070855596065\\
4	1.1713310546201\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.633626542983812\\
2	0.829836144183102\\
3	0.976226628588797\\
4	1.35354289111746\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,1.237in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00167790645812327\\
2	0.00228016548777977\\
3	0.00318742185439004\\
4	0.00462726511721075\\
5	0.00716743728878421\\
6	0.0129273763723776\\
7	0.0308460700090715\\
8	0.115533318647694\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.603245855871981\\
2	0.755456602981771\\
3	0.858512489463287\\
4	0.953124795407537\\
5	1.02704466315581\\
6	1.08592420449446\\
7	1.13090925633169\\
8	1.18526539633296\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.521in,
height=0.544in,
at={(0.758in,0.481in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000617491691008369\\
2	0.000717776254822589\\
3	0.000835285279992789\\
4	0.000979591082427033\\
5	0.00115487030006212\\
6	0.00136293515999463\\
7	0.00161619354701616\\
8	0.00191279748068678\\
9	0.00227218304658774\\
10	0.0026908090305821\\
11	0.00319938829308565\\
12	0.00381122202979217\\
13	0.00474535479665619\\
14	0.00756353464992525\\
15	0.017474797658002\\
16	0.0547436973724798\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.418853266349202\\
2	0.478839773751748\\
3	0.529812149718329\\
4	0.573539152412764\\
5	0.611663102441733\\
6	0.642886720358442\\
7	0.677359347479036\\
8	0.701877932539796\\
9	0.729554340449397\\
10	0.748421821359951\\
11	0.768367609874633\\
12	0.782658242865203\\
13	0.796571330906253\\
14	0.806933582871612\\
15	0.818312174451126\\
16	0.833414484583038\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%

>>>>

\begin{axis}[%
width=4.036in,
height=0.485in,
at={(0.677in,3.369in)},
scale only axis,
xmin=0,
xmax=2,
xtick={1},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
legend style={legend cell align=left, align=left, draw=white!15!black},
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}] table[row sep=crcr] {%
1	2.82172701256397\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_I$}

\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}] table[row sep=crcr] {%
1	0.000265479925168544\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
2	0\\
};
\addlegendentry{$s_P$}

@@

\begin{axis}[%
width=4.036in,
height=0.485in,
at={(0.677in,2.641in)},
scale only axis,
xmin=0,
xmax=3,
xtick={1, 2},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.305941511463392\\
2	2.76242712267536\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	6.71549962409912e-06\\
2	6.78915225846286e-06\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
3	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.485in,
at={(0.677in,1.914in)},
scale only axis,
xmin=0,
xmax=5,
xtick={1, 2, 3, 4},
ymin=0,
ylabel style={font=\color{white!15!black}},
ylabel={Waveform amplitude},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.007350356637722\\
2	0.0147094858376509\\
3	0.0590793778157153\\
4	1.02788897323282\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.711002949351241\\
2	0.867986174604486\\
3	1.02417325240103\\
4	1.34410968002342\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
5	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.485in,
at={(0.677in,1.186in)},
scale only axis,
xmin=0,
xmax=9,
xtick={1, 2, 3, 4, 5, 6, 7, 8},
ymin=0,
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.00126526562881413\\
2	0.00163389424667508\\
3	0.00214228814037994\\
4	0.00291473026101762\\
5	0.00404484067642897\\
6	0.00591327046970132\\
7	0.0122792439934077\\
8	0.0818816961284654\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.633029580480129\\
2	0.771481626745736\\
3	0.873536833990131\\
4	0.968051760825038\\
5	1.03324782087805\\
6	1.09291316442134\\
7	1.12974439643375\\
8	1.17077692579217\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
9	0\\
};
\end{axis}

\begin{axis}[%
width=4.036in,
height=0.485in,
at={(0.677in,0.458in)},
scale only axis,
xmin=0,
xmax=17,
xtick={ 1,  2,  3,  4,  5,  6,  7,  8,  9, 10, 11, 12, 13, 14, 15, 16},
xlabel style={font=\color{white!15!black}},
xlabel={Sorted subband index},
ymin=0,
ytick={  0, 0.4, 0.8},
axis background/.style={fill=white},
xmajorgrids,
ymajorgrids,
title style={font=\huge}, label style={font=\huge}, ticklabel style={font=\LARGE}, legend style={font=\LARGE}
]
\addplot[ycomb, color=mycolor1, line width=2.0pt, mark=o, mark options={solid, mycolor1}, forget plot] table[row sep=crcr] {%
1	0.000465023983221312\\
2	0.00052438501576905\\
3	0.000598178789998686\\
4	0.000676629883061283\\
5	0.000779645514114207\\
6	0.000891058787067234\\
7	0.00103482618212732\\
8	0.00120004374054558\\
9	0.00140039988214198\\
10	0.00164300972889049\\
11	0.00194088588142548\\
12	0.00233328546477028\\
13	0.00288323717596057\\
14	0.0036883861713129\\
15	0.00495722356981356\\
16	0.00703735366203068\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\addplot[ycomb, color=mycolor2, line width=2.0pt, mark=x, mark options={solid, mycolor2}, forget plot] table[row sep=crcr] {%
1	0.429987185652732\\
2	0.486975650168299\\
3	0.533174859894872\\
4	0.576333984439071\\
5	0.61391168211896\\
6	0.648236185996695\\
7	0.680465320861151\\
8	0.708130047574106\\
9	0.735885034607608\\
10	0.758476599592402\\
11	0.780983741629149\\
12	0.797703057712941\\
13	0.813882700419696\\
14	0.824241120475894\\
15	0.832517663389794\\
16	0.8354347465423\\
};
\addplot[forget plot, color=white!15!black, line width=2.0pt] table[row sep=crcr] {%
0	0\\
17	0\\
};
\end{axis}
\end{tikzpicture}%
